---
title: "How To Use?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{howToUse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lrmodel)
```

## Introduction
*lrmodel* package is designed to fit linear models for both simple and multiple linear regressions as well as conduct ANOVA on a given data set. 

## Example of running lr function
```{r}
m <- lr(mpg ~ hp + wt, mtcars)
```

We can check out the detailed information by `summary_lr(...)` function.
```{r}
summary_lr(m)
```

Additionally, it has `prediction(...)` function which enables you to further predicting any new data with the trained model.

```{r}
new_data <- data.frame(hp = c(110), wt = c(3.521))
p <- prediction(m, new_data)
```

## Example of conducting ANOVA
We can obtain the ANOVA table by calling `anova(...)` function.
```{r}
a <- anova(mpg ~ hp + wt, mtcars)
```

## Evalution
*lrmodel* package is evaluated by comparing with `lm(...)` function and `aov(...)` function respectively in terms of efficiency and correctness.
```{r}
start <- Sys.time()
lr(mpg ~ hp + wt, mtcars)
stop <- Sys.time()
execution <- stop - start
print(paste("lr function execution time:", execution[[1]]))

start <- Sys.time()
lm(mpg ~ hp + wt, mtcars)
stop <- Sys.time()
execution <- stop - start
print(paste("lm function execution time:", execution[[1]]))

```
We observed that the two functions have identical outputs and negligible run time difference.

```{r}
start <- Sys.time()
anova(mpg ~ hp + wt, mtcars)
stop <- Sys.time()
execution <- stop - start
print(paste("anova function execution time:", execution[[1]]))

start <- Sys.time()
aov(mpg ~ hp + wt, mtcars)
stop <- Sys.time()
execution <- stop - start
print(paste("aov function execution time:", execution[[1]]))
```
We observed that function `anova(...)` and function `aov(...)` have highly similar outputs and negligible run time difference.
